---
title: "Final Project"
author: "Claire Fridkin"
date: "10/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
library(knitr)
```


###**Precis**

At this point, for my final project, I plan to analyze the career (the rise, the fall, the highs, the lows, whatever I can discern) of my favorite actor, Nicolas Cage. I contacted a former FiveThirtyEight employee who wrote culture/lifestyle articles, and he was able to provide me with some base data on Nicolas Cage movies. I may obtain more later, we will see, but I have a pretty reasonable amount to start analyzing data. Below, I'll provide some simple summary stats and tables. 

**Summary**

```{r}
data <- read_excel("NIC CAGE.xlsx") %>%
  clean_names()
summary(data)
```

**Sample Table**
```{r}
sampletable <- data %>%
  select(movie, total_box_office) %>%
  arrange(desc(total_box_office)) %>%
  slice(1:5)

sampletable %>%
  kable(caption = "Top 5 Grossing Nicolas Cage Movies") 


```

